Spec2Fab: A High-Fidelity Mapping from Specification to Fabrication

### 2012-08-02 paper.tex
castics example

\section{Experiments}
\section{Print Material Characterization and Measurement}

\subsection{Previous Work}
Subsurface scattering. Mechanical properties
A material with a particular
look and deformation properties is shown in Figure~\ref{fig:deform}

>>>>

\section{Experiments}
\subsection{Print Material Characterization and Measurement}

\subsection{Subsurface Scattering, Deformation and Mass}
Combining previous work on replicating
subsurface scattering and deformation behavior, 
we produced
material with a particular
look and deformation properties as shown in Figure~\ref{fig:deform}.
We als considered one additional property:mass. In this example, we
tried to make the material as light as possible.
\section{Caustics for a Mesh}
We demonstrate how to produce a 3D model with specific caustic shape under a particular lighting,
similar to \cite{Finckh:2010}. The difference is that we optimize on an arbitrary 3D model,
and we use a generic rendering package (NVidia optiX). Our algorithm took 6 hours to finish
with $4000$ spline control points for the model and $600\times 600$ resolution for the caustic image. A 
picture of our printed result under desired lighting is shown in Figure~\ref{fig:caustic}.
